%\clearpage
%
\recipient{Dr. Tahmeed M. Al-Hussaini}{Director\\BUET-Japan Institute of Disaster Prevention \& Urban Safety (BUET-JIDPUS)\\Bangladesh University of Engineering \& Technology (BUET), Dhaka - 1000 \& \\Sub-Project Manager (CP-3140:HEQEP AIF 3$^{rd}$ Round} % Letter recipient
\date{\today} % Letter date
\opening{Sir,} % Opening greeting
\closing{\hfill \break Sincerely,} % Closing phrase
\enclosure[Attached (Submitted as Hard Copy)]{\begin{enumerate} 
	\item Curriculum Vit\ae{}
	\item Copy of SSC Examination Certificate
	\item Copy of HSC Examination Certificate
	\item Copy of Provisional Certificate of B.Sc. in Civil Engineering Degree
\end{enumerate}
}
% List of enclosed documents

\makelettertitle % Print letter title
%letter body goes here
From an announcement published on the website of BUET-Japan Institute of Disaster Prevention and Urban Safety (BUET-JIDPUS), it came to my knowledge that, BUET-JIDPUS is offering a few Research Fellowship opportunity for Post-Graduate Students. I have recently obtained my B.Sc in Civil Engineering degree from Bangladesh University of Engineering and Technology (BUET) and currently pursuing M.Sc. Engg. (Civil \& Structural Engineering) from the same institution as a full-time student. 

In pursue of my B.Sc. in Civil Engineering degree, I have completed a 4.5 credit-hour thesis work securing the highest grade. The work was focused on determining the non-linear behavior of  original and jacketed reinforced concrete sections in inelastic response zone. It was also a first step to develop an evaluation method for seismic retrofitting by column jacketing. Although briefly, in course of my study into the Earthquake Engineering, I have also explored the area of earthquake related disasters and their management. In light of these experiences, an opportunity to contribute as a research fellow in a project aimed at developing Post-Graduate research and degree programs in Disaster Risk Reduction is a very lucrative opportunity and I would like to present myself as a candidate.  

My detailed CV and copy of all academic certificates are attached with this letter. If I can provide you with any further information on my background and qualifications, please let me know. I am  looking forward to hear from you.

\makeletterclosing % Print letter signature
\clearpage
